---
title: "Fandom Association with Loneliness Analysis"
author: "Jack Wang"
output:
  word_document:
    toc: true
  html_document:
    toc: true
    code_folding: show
---
#Data_collection_analysis_fandom

The group work on the analysis of correlations between interactions in fandom and the level of loneliness.
Here we import the csv dataset into the RStudio software first.


```{r}

library(dplyr)
library(readr)
library(ggplot2)
d_loneliness_association <- read.csv('Loneliness_association.csv')

```


First, we exclude all the answers that say they don't follow any celebrities in real life.


```{r}

d_loneliness_association <- d_loneliness_association %>%
  filter(
    Follow_celeb == 'Yes.'
  )

```


Then we could then convert all our ordinal answers into numerical forms that allow us to add up and summarise the scores.
Here, we sort out the series of questions that test the loneliness, L_C1 - L_C8, with two reverse questions. Here the higher the score is, the higher the loneliness level would be.


```{r}

normal_questions <- c('L_C1', 'L_C2', 'L_C4', 'L_C5', 'L_C7', 'L_C8')
reverse_questions <- c('L_C3', 'L_C6')
d_loneliness_association <- d_loneliness_association%>%
  mutate(
    across(
      all_of(normal_questions),
      ~case_when(
        . == 'Never' ~ 1,
        . == 'Rarely' ~ 2,
        . == 'Sometimes' ~ 3,
        . == 'Often' ~ 4,
        TRUE ~ NA_real_
      ),
      .names = "{.col}_num"
    ),
    across(
      all_of(reverse_questions),
      ~case_when(
        . == 'Never' ~ 4,
        . == 'Rarely' ~ 3,
        . == 'Sometimes' ~ 2,
        . == 'Often' ~ 1,
        TRUE ~ NA_real_
      ),
      .names = "{.col}_num"
    )
  )

```
---
Here we then clean out the questions on the participation with fandom, marked F_C1 - F_C7, with no reverse questions. Here, the higher the scores are, the more participated you are in the fandoms.
---

```{r}

questions <- c('F_C1', 'F_C2', 'F_C3', 'F_C4', 'F_C5', 'F_C6', 'F_C7')
d_loneliness_association <- d_loneliness_association%>%
  mutate(
    across(
      all_of(questions),
      ~case_when(
        .== "Strongly disagree" ~ 1,
        .== "Disagree" ~ 2,
        .== "Neutral" ~ 3,
        .== "Agree" ~ 4,
        .== "Strongly agree" ~ 5,
        TRUE ~ NA_real_
      ),
      .names = "{.col}_num"
    )
  )

```

Then we can sum up all the columns together to get two overall scores.

```{r}
d_loneliness_association <- d_loneliness_association%>%
  mutate(
    frequency_score = rowSums(
      across(all_of(paste0(c(normal_questions, reverse_questions), "_num"))),
      na.rm = TRUE
  ),
  agreement_score = rowSums(
      across(all_of(paste0(c(questions), "_num"))),
      na.rm = TRUE
    )
  )
```

After the cleaning, we can see the distribution of gender and age respectively, starting with gender first, then age groups.
The gender is done only on biological gender instead of the identity.
We could also calculate the mean of both scores to see the average participation level and the average degree of loneliness.


```{r}
library(psych)

Frequency_questions_num <- c('L_C1_num', 'L_C2_num', 'L_C3_num', 'L_C4_num', 'L_C5_num','L_C6_num', 'L_C7_num', 'L_C8_num')
Agreement_questions_num <- c('F_C1_num', 'F_C2_num', 'F_C3_num', 'F_C4_num', 'F_C5_num', 'F_C6_num', 'F_C7_num')
psych::alpha(d_loneliness_association[, Frequency_questions_num])

psych::alpha(d_loneliness_association[, Agreement_questions_num])
```

```{r}
d_loneliness_association %>%
  group_by(
    Gender
  ) %>%summarise(
    n = n(),
    M1 = mean(frequency_score),
    M2 = mean(agreement_score)
    )
```

Here above we can see that there is only 1 male participant.

```{r}
d_loneliness_association %>%
  group_by(
    Age_group
  ) %>%summarise(
    n = n(),
    M1 = mean(frequency_score),
    M2 = mean(agreement_score),
    SD1 = sd(frequency_score),
    SD2 = sd(agreement_score),
    MED1 = median(frequency_score),
    MED2 = median(agreement_score)
    )
```

```{r}

d_loneliness_association %>%
  ggplot(
      aes(x = frequency_score, y = agreement_score)
  ) + 
  geom_jitter() +
  labs(
    title = "Correlation between loneliness and fandom participation",
      x = "loneliness_score",
      y = "fandom_participation_score"
  )
```

```{r}
d_loneliness_association %>%
  cor.test(
    ~ agreement_score + frequency_score,
    data = .
  )
```

```{r}
d_loneliness_association %>%
  cor.test(
    ~ agreement_score + frequency_score,
    data = .,
    method = "spearman"
  )
```
